---
title: "04_function_plotting_incucyte"
author: "Maria Dermit"
date: "23/10/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading libraries
```{r}
library(tidyverse)
#install.packages("datapasta")
library(datapasta) #CP data into R 
```

### Pasting the file 

Demonstrate the datapasta tools for data Copy-Pasta

```{r}
plus_raw<-tibble::tribble(
  ~`RNAiMAX.5.nM,HCT116plus.(1).10K./.well`, ~`Con.si.5.nM,HCT116plus.(1).10K./.well`, ~`C1.si.5.nM,HCT116plus.(1).10K./.well`, ~`RNAiMAX.5.nM,HCT116+.(1).10K./.well`, ~`Con.si.5.nM,HCT116+.(1).10K./.well`, ~`C1.si.5.nM,HCT116+.(1).10K./.well`, ~`RNAiMAX.5.nM,HCT116+.(1).10K./.well`, ~`Con.si.5.nM,HCT116+.(1).10K./.well`, ~`C1.si.5.nM,HCT116+.(1).10K./.well`,
                                   8.317347,                                 8.113516,                                8.515937,                               10.07654,                              9.076317,                              8.47286,                               4.736556,                              5.000928,                             5.138074,
                                   9.220201,                                 8.756005,                                9.366104,                               11.22823,                              9.622458,                             8.834867,                               4.960054,                              5.168535,                             5.165822,
                                   10.24604,                                 9.467433,                                10.08666,                               11.88028,                              10.30522,                             9.198041,                               5.247811,                              5.351867,                             5.855083,
                                   11.14086,                                   10.258,                                10.72866,                               12.11746,                              9.876403,                             8.473389,                               5.667076,                              5.911754,                             5.925839,
                                   11.69871,                                 10.55528,                                11.21601,                               12.78979,                              10.23073,                             8.504484,                               6.052967,                              6.200076,                             6.452169,
                                   12.53814,                                 11.12362,                                11.73229,                               13.46051,                              10.61954,                             8.562291,                               6.421977,                              6.538721,                             6.539765,
                                   13.04459,                                 11.73378,                                12.05706,                               14.23695,                               11.0761,                             8.614766,                               6.965345,                              6.791482,                             6.623363,
                                   14.15729,                                   12.375,                                12.83863,                               15.21379,                              11.54568,                             8.747778,                               7.429229,                              7.219109,                              6.90092,
                                   16.12349,                                 14.01904,                                 14.4405,                               17.95497,                              14.32431,                             12.20275,                                8.19553,                               8.05402,                             7.360847,
                                   17.07406,                                 14.45902,                                14.80498,                                 17.933,                              14.14988,                             10.68987,                               8.822061,                              8.245361,                              7.63392,
                                   18.09781,                                 15.22801,                                14.99377,                               18.89297,                              14.10084,                             9.485605,                               10.38992,                              9.620574,                             8.761279,
                                   19.76006,                                  16.6323,                                 16.1113,                               20.09795,                              14.89565,                             9.188794,                               11.48161,                              10.55528,                             9.743731,
                                   21.14177,                                 17.37129,                                16.36347,                               21.68695,                              16.05973,                             9.105255,                                12.5224,                               11.2954,                              9.31161,
                                   22.88517,                                 18.47341,                                16.73756,                                23.5996,                              17.05556,                             8.926695,                               13.40662,                              11.59334,                             8.978297,
                                   24.98919,                                 19.75264,                                17.30589,                               25.65162,                              18.17992,                             8.634168,                               14.76203,                              11.91428,                             8.735765,
                                   27.52048,                                 21.26222,                                17.91563,                               28.04747,                              19.64432,                             8.609048,                               16.44266,                              12.79777,                             8.871441,
                                   30.92387,                                 23.46428,                                20.00747,                               30.74251,                              21.23302,                             8.431431,                               18.29368,                              13.86093,                             8.877079,
                                   34.05448,                                 25.46332,                                20.62971,                               33.83632,                              23.28214,                             9.353817,                               21.37146,                              15.96416,                             11.09249,
                                   37.09359,                                 26.98089,                                19.93385,                                37.1664,                              25.56893,                             9.132969,                               22.48351,                              16.16215,                             9.447023,
                                   40.48071,                                 28.75672,                                 19.7597,                               40.40938,                              26.92311,                             7.763707,                               26.59857,                              18.77145,                              11.7202,
                                   44.94362,                                 31.38993,                                20.38434,                               46.14558,                              31.91995,                             16.87586,                               28.78369,                              19.41825,                             11.17349,
                                   49.58646,                                 34.31292,                                21.17954,                                47.6261,                                32.752,                             13.56206,                               31.42488,                              19.88985,                             10.79632,
                                   54.41776,                                 37.42363,                                 22.1414,                               50.14784,                               35.0508,                             12.11188,                               34.67614,                              21.86353,                             10.26021,
                                   59.09588,                                 40.96466,                                 23.1929,                               52.43291,                              37.38717,                             11.29972,                               37.51614,                              23.57569,                             10.11707,
                                   63.35794,                                 44.36053,                                24.06071,                               54.56837,                              39.68808,                             10.75309,                               41.28076,                              24.97292,                             10.02369,
                                   67.20863,                                 47.94794,                                25.14177,                               56.56934,                              42.21008,                             10.51188,                               45.02403,                              28.87614,                             16.18644,
                                   70.49752,                                  50.7468,                                26.25242,                               58.24501,                              44.92739,                             10.27115,                               48.99892,                              31.14983,                             16.07569,
                                   73.20787,                                 54.17266,                                  27.406,                               59.62133,                              47.31668,                             10.04498,                               49.32714,                              31.01793,                             11.03533,
                                   75.73478,                                 57.05143,                                28.71516,                               60.81629,                               49.6349,                             9.877542,                               51.75282,                              32.29439,                             10.78915,
                                   77.64987,                                 59.61332,                                30.05981,                               61.58921,                              51.92357,                             9.726385,                               54.08704,                              33.91307,                              10.3805,
                                   79.32023,                                 62.19166,                                31.44836,                               62.20423,                              53.94661,                             9.513864,                               55.52265,                              36.60162,                             10.53658,
                                   80.67471,                                 64.26923,                                33.01418,                               62.52013,                              55.86336,                             9.424447,                               56.87163,                              37.85831,                             10.43082,
                                   81.67416,                                 66.27381,                                34.55596,                               65.34884,                                45.454,                             4.406401,                               58.42373,                              39.66949,                             10.33206
  )

```

```{r}
minus_raw<-tibble::tribble(
  ~`RNAiMAX.5.nM,HCT116-/-.(7).10K./.well`, ~`Con.si.5.nM,HCT116-/-.(7).10K./.well`, ~`C1.si.5.nM,HCT116-/-.(7).10K./.well`, ~`RNAiMAX.5.nM,HCT116-/-.(1).7K./.well`, ~`Con.si.5.nM,HCT116-/-.(1).7K./.well`, ~`C1.si.5.nM,HCT116-/-.(1).7K./.well`, ~`RNAiMAX.5.nM,HCT116-/-.(1).10K./.well`, ~`Con.si.5.nM,HCT116-/-.(1).10K./.well`, ~`C1.si.5.nM,HCT116-/-.(1).10K./.well`,
                                   9.81912,                                8.615961,                               8.751816,                                4.733108,                               4.300678,                              3.482718,                                 14.93489,                                14.83685,                               10.43327,
                                  10.81173,                                9.376701,                               9.609836,                                5.064928,                               4.406344,                              3.562474,                                 16.42298,                                16.12094,                               10.79348,
                                  12.08134,                                10.12392,                               10.56952,                                5.297894,                               4.575052,                              3.686055,                                 18.22569,                                17.56539,                               11.59804,
                                  13.43103,                                10.94175,                                11.6491,                                5.357785,                               4.515712,                              3.385401,                                 20.41986,                                19.74416,                               12.26088,
                                  14.41808,                                11.48878,                               12.48388,                                5.490437,                                4.50407,                              3.395997,                                 22.72536,                                21.37012,                               13.02599,
                                  15.77509,                                12.25566,                               13.56638,                                 5.73451,                                4.56882,                              3.443298,                                  24.8508,                                23.42756,                               13.22645,
                                  16.90257,                                12.88445,                               14.67539,                                5.961894,                               4.668357,                              3.388932,                                  27.5409,                                25.62979,                               13.63076,
                                  18.64239,                                13.90025,                               15.96811,                                6.282554,                               4.740286,                              3.360096,                                  30.3524,                                28.40868,                               14.14261,
                                  21.87864,                                16.24044,                               18.26421,                                7.537505,                               5.727373,                              4.623585,                                 33.43636,                                31.42241,                               14.40162,
                                  23.37314,                                16.77049,                               19.62414,                                7.315278,                               5.248772,                              3.769965,                                 36.89765,                                33.72434,                               14.55361,
                                  25.57339,                                17.63065,                               20.65092,                                7.520343,                               5.084004,                              3.473985,                                 41.69929,                                37.42862,                               16.90441,
                                  29.26926,                                20.23758,                               23.49119,                                7.958607,                               5.237017,                              3.488369,                                 45.89936,                                40.69178,                               17.72398,
                                  31.70776,                                21.09325,                               24.77568,                                8.604507,                                5.50344,                              3.439372,                                 51.61116,                                44.77087,                               17.97285,
                                  35.08344,                                22.90537,                               27.04443,                                9.247269,                               5.640305,                              3.373731,                                 58.14962,                                 48.5812,                                16.5668,
                                  39.18853,                                24.77456,                               29.69305,                                10.01134,                               6.012549,                              3.400885,                                 65.12557,                                53.80603,                               16.06385,
                                  43.44593,                                26.99159,                               32.31179,                                11.08064,                                6.25512,                              3.455365,                                 71.41685,                                58.83381,                               15.44275,
                                  49.02388,                                30.83938,                               35.93959,                                12.14944,                               6.762946,                               3.53002,                                 77.24747,                                64.22731,                               15.17076,
                                  53.96994,                                34.20393,                               39.15318,                                13.47386,                               7.309945,                              4.346281,                                 83.13422,                                71.30856,                               18.79276,
                                  57.45261,                                36.00571,                               41.02694,                                15.09909,                               8.036278,                              4.024107,                                 85.60373,                                73.43707,                               14.70422,
                                  61.61481,                                38.78048,                               43.94714,                                16.33275,                               8.036646,                              3.586887,                                 89.06828,                                77.90636,                               19.89475,
                                   65.7233,                                42.13379,                               47.22622,                                19.32783,                               10.80435,                              5.898232,                                 91.32195,                                81.44012,                               20.09682,
                                  69.32917,                                45.44127,                               50.51954,                                20.36909,                               9.927887,                              4.536535,                                 92.65312,                                82.86722,                               17.01838,
                                   72.7113,                                48.49699,                               53.59412,                                22.28186,                               9.973045,                              4.212115,                                  93.6778,                                 85.6106,                               15.46976,
                                  75.57817,                                51.42204,                                56.2566,                                24.57076,                               10.41617,                              3.872648,                                 94.49564,                                87.56981,                               14.26568,
                                  78.31065,                                54.24413,                               58.83677,                                 26.9402,                               10.99911,                              3.780375,                                  95.1281,                                89.05927,                               13.61248,
                                  80.79825,                                56.85513,                               61.16121,                                29.43505,                               11.69949,                              3.715116,                                 95.64413,                                90.81101,                               18.29616,
                                   82.8268,                                59.25398,                               63.20044,                                31.88462,                               12.46807,                              3.686365,                                  95.7002,                                91.26796,                               15.71162,
                                  84.64217,                                61.41418,                               64.97432,                                34.34223,                               13.34613,                              3.754182,                                 95.52353,                                 92.3654,                               12.44031,
                                  85.86633,                                63.23475,                               66.50603,                                36.73535,                               14.25598,                              3.682351,                                 95.24211,                                92.83736,                               11.99305,
                                  86.85645,                                64.98224,                               67.80051,                                38.97519,                               15.35465,                              3.697879,                                 95.06066,                                93.39899,                               11.69039,
                                  87.38974,                                 66.4443,                               68.80438,                                40.97858,                               16.52303,                              3.741324,                                 94.98737,                                94.02058,                                11.4886,
                                  87.87897,                                67.70695,                               69.74599,                                43.09551,                               17.84767,                              3.756922,                                 94.76224,                                94.62884,                               11.29745,
                                  88.27973,                                68.84965,                               70.55021,                                45.07098,                               19.06933,                              3.801639,                                 94.81008,                                94.75134,                               11.09607
  )

```


There are 3 experiments on each data set; lets do mean and SD and do a pretty plot. 

```{r}
plus_raw %>% names()

```

```{r}
std <- function(x) sd(x)/sqrt(length(x))
```

```{r}
plus_long <- plus_raw %>% 
 pivot_longer(everything(),names_to="exp", values_to="values") %>% 
 mutate(exp = case_when( str_detect(exp,"RNAiMAX") ~ "RNAiMAX",
                         str_detect(exp,"Con.si") ~ "Con.si",
                         str_detect(exp,"C1.si") ~ "C1.si")) %>% 
 mutate(rep= rep(rep(seq(1, 3, 1), each=3),33)) %>% 
 mutate(elaps=rep(seq(0, 96, 3), each=9)) %>% 
 group_by(exp,elaps) %>% 
 summarise(mean_confluency=mean(values), 
           sem_confluency=std(values) ) %>% 
  mutate(condition="plus")

minus_long <- minus_raw %>% 
 pivot_longer(everything(),names_to="exp", values_to="values") %>% 
 mutate(exp = case_when( str_detect(exp,"RNAiMAX") ~ "RNAiMAX",
                         str_detect(exp,"Con.si") ~ "Con.si",
                         str_detect(exp,"C1.si") ~ "C1.si")) %>% 
 mutate(rep= rep(rep(seq(1, 3, 1), each=3),33)) %>% 
 mutate(elaps=rep(seq(0, 96, 3), each=9)) %>% 
 group_by(exp,elaps) %>% 
 summarise(mean_confluency=mean(values), 
           sem_confluency=std(values) ) %>% 
  mutate(condition="minus")

```

Now we can combine these two tidy data:

```{r}
all_incucyte_data<-rbind(plus_long, minus_long)
```

Lets plot this! Remember that in lesson 2 we learnt the order of facet:

[Grammar of graphics](https://github.com/demar01/R-NA/blob/master/slides/02-wrangle_visualise_rtqPCR/img/grammar-of-graphics.png)

```{r}
all_incucyte_data %>%  #data
ggplot(aes(x=elaps, y=mean_confluency,color = exp, group=exp))+ #aesthetic 
 geom_line(size=1) + #geom
  geom_point(size=4)+ #geom
 scale_colour_manual(values=c(C1.si="#000066",Con.si="#663399",RNAiMAX="#339999")) +

  geom_errorbar(aes(ymin=mean_confluency, ymax=mean_confluency+sem_confluency),         width=0.5,  position=position_dodge(0.05)) + #geom
  facet_wrap(~condition)+ #facets
  ylim(0,100)+  #coord
  xlab("Time (h)")+  #coord
    ylab("Confluency (%)") + #coord+
    theme_classic()+ #theme
    theme(strip.text.x = element_text(size=10))+
theme(axis.text.x = element_text(size =10),
axis.text.y = element_text(size =10),
axis.title.x = element_text(size =10),
axis.title.y = element_text(size =10), 
legend.title =  element_text(size =0),
legend.text = element_text(size = 10),
legend.position = "top")
  
```

We can calculate when the confluence starts to be different across different treatment:
```{r}
plus_raw %>% 
 pivot_longer(everything(),names_to="exp", values_to="values") %>% 
 mutate(exp = case_when( str_detect(exp,"RNAiMAX") ~ "RNAiMAX",
                         str_detect(exp,"Con.si") ~ "Con.si",
                         str_detect(exp,"C1.si") ~ "C1.si")) %>% 
 mutate(rep= rep(rep(seq(1, 3, 1), each=3),33)) %>% 
 mutate(elaps=as.character(rep(seq(0, 96, 3), each=9))) %>% 
  group_by(exp,elaps) %>% 
  summarise(value = list(values)) %>% 
  spread(exp,value) %>% 
  group_by(elaps) %>% 
  mutate(p_value = t.test(unlist(RNAiMAX), unlist(C1.si ))$p.value) %>% 
  filter(p_value<0.05)
```

As early as 50 h the confluence % start to be different. We can annotate the plot to show this difference. Note that we have done quaick t.test across all timepoints.   

```{r}
all_incucyte_data %>%  #data
   filter(condition=="plus") %>% 
ggplot(aes(x=elaps, y=mean_confluency,color = exp, group=exp))+ #aesthetic 
 geom_line(size=2) + #geom
  geom_point(size=2)+ #geom
 scale_colour_manual(values=c(C1.si="#000066",Con.si="#663399",RNAiMAX="#339999")) +

  geom_errorbar(aes(ymin=mean_confluency, ymax=mean_confluency+sem_confluency),                        width=0.2,  position=position_dodge(0.05)) + #geom
  ylim(0,100)+  #coord
  xlab("Time (h)")+  #coord
    ylab("Confluency (%)") + #coord+
    theme_minimal()+ #theme
    theme(strip.text.x = element_text(size=10))+
theme(axis.text.x = element_text(size =10),
axis.text.y = element_text(size =10),
axis.title.x = element_text(size =10),
axis.title.y = element_text(size =10), 
legend.title =  element_text(size =0),
legend.text = element_text(size = 10),
legend.position = "top")+
  annotate("text", x = 51, y = 5, label = "*", size=8, color="#000066")+
  ggsave(here::here("slides","04-incucyte", "plots", "plus.png"))

```
  

