---
title: "03_function_imput_raw_rtqpcr"
author: "Maria Dermit"
date: "13/10/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading libraries
```{r}
library(tidyverse)
library(readxl) #this package let us read an excel file into R
library(here) #this package let us organise files in path easily
```

### Reading the excel file

```{r}
rtpcr_data_raw <- read_excel(here("slides","03-raw_rtqPCR_functions","data", "C1_HCT116plus_180820rep_data.xls"),
sheet = 1, na = "Undetermined",
skip = 7, n_max = 72)
```

Kalis RT-qPCR data consist of two experiements:\
1:\
Cells max\
Con si (control) \
C1 si\
2:\
Cells max \ 
LNA A (control)\ 
LNA 1\
LNA 2\ 

She did these two experiments with two sets of primers: 2-3 primers and C1 protein. Her housekeeping control are two: GAPDH and RPS18 and she usually does the mean of the two for the delta Ct.

So in the `rtpcr_data_raw` data that we read the columns we can select the columns we   are  interested in:
```{r}
rtpcr_data_mean_CT <- rtpcr_data_raw %>% 
  select( "Sample"="Sample Name", "Target"="Target Name", "CT" = "Cт") %>% 
  arrange(Sample, Target) %>% 
 filter(!(Sample=="LNA 1" & Target=="GAPDH" & CT >20)) %>% 
  group_by(Sample,Target) %>% 
  summarise(meanCT=mean(CT)) %>% 
  spread(Target,meanCT) %>% 
  gather(Target, meanCT, -Sample, -GAPDH,-RPS18) %>% 
   group_by(Sample)%>%
   mutate(housekeeping=(GAPDH+RPS18)/2) %>% 
  select(-GAPDH,-RPS18)
```

This is a relative complex number of steps so we could automate them writing a function like so:
```{r}
get_CT_housekeeping <- function(x,mytarget,mythreshold){
  x %>% 
    if(){
      
    }
  select( "Sample" = "Sample Name", "Target" = "Target Name", "CT" = "Cт") %>%
  arrange(Sample, Target) %>% 
  filter(!(Target==mytarget)) %>% 
  filter(!(Sample=="LNA 1" & Target==mytarget & CT >mythreshold)) %>% 
  group_by(Sample,Target) %>% 
  summarise(meanCT=mean(CT)) %>% 
  spread(Target,meanCT) %>% 
  gather(Target, meanCT, -Sample, -GAPDH,-RPS18) %>% 
  group_by(Sample)%>%
  mutate(housekeeping=(GAPDH+RPS18)/2) %>% 
  select(-GAPDH,-RPS18)
}
```
And then we input our `rtpcr_data_raw` into the function like so:
```{r}
rtpcr_data_mean_CT <- get_CT_housekeeping(rtpcr_data_raw,"C1 protein",mythreshold=20)

```

There were some values that came as "Undetermined" in the raw data, we can transform those to CT value 40 (aka high CT values).
```{r}
rtpcr_data_mean_CT$meanCT[is.na(rtpcr_data_mean_CT$meanCT)]=40
```


### Calculate Δ Ct
```{r}
rtpcr_data_deltaCT <- rtpcr_data_mean_CT %>%
  mutate(deltaCT = meanCT - housekeeping)
```

Control samples are Con si. We  need to calculate the mean ΔCt of the two different targets (2_3 & C1) that Kali tested.
```{r}
#Calculate ΔΔCt   
Control_average_2_3<- rtpcr_data_deltaCT %>%
  as_tibble() %>% 
  mutate_if(is.character,as.factor) %>% 
  filter(str_detect(Sample, c("Con si","LNA A")) &     str_detect(Target, "2-3")) %>%
   pull(deltaCT)

Control_average_C1<- rtpcr_data_deltaCT %>%
  as_tibble() %>% 
  mutate_if(is.character,as.factor) %>% 
  filter(str_detect(Sample, c("Con si","LNA A")) & str_detect(Target, "protein")) %>%
   pull(deltaCT)

```

We can now calculate ΔΔCt:
```{r}
deltadeltaCT <- rtpcr_data_deltaCT %>%
  mutate(ddCT = case_when(
    Target == "C1 2-3" & str_detect(Sample,"LNA") ~
      deltaCT -     Control_average_2_3[2],
     Target == "C1 2-3" & str_detect(Sample,"LNA", negate=TRUE) ~        deltaCT - Control_average_2_3[1],
    Target == "C1 protein" & str_detect(Sample,"LNA") ~
      deltaCT - Control_average_C1[2],
  Target == "C1 protein" & str_detect(Sample,"LNA", negate=TRUE) ~
      deltaCT - Control_average_C1[1]
  ))
```

And we can calculate expression values:

```{r}
expression_values<- deltadeltaCT %>%
  mutate(expression = 2^(-ddCT)) %>% 
  mutate_if(is.character,as.factor)
#Creating this column to short column order in plot
expression_values$rep=c(1:12)
```

We can now plot the expression values
```{r}
expression_plot<-expression_values %>% 
    arrange(-rep) %>% 
    ggplot(aes(x =  fct_inorder(Sample), y = expression, fill = Target)) +
    geom_col(position = position_dodge(1))+
  xlab("Sample")
```

We could save this plot. Initially we create a folder inside our session 3:

```{r}
suppressWarnings(dir.create(paste0(paste0(here(),"/slides","/03-raw_rtqPCR_functions"),"/plots")))
```

And then we can save the plot with:

```{r}
expression_plot+  ggsave(here("slides", "03-raw_rtqPCR_functions","plots","expression_plot.png"))
```

### Concluding remarks

There is anoter RT-qPCR in the `data` folder of this session called `HCT116plus_RNAi_LNA_180920_data.xls`. Could you represent the expresion values of this experiment? Could you write additional functinos to further automate RT-qPCR representation? 


