---
title: "02_wrangling_visualising_rtqpcr"
author: "Maria Dermit"
date: "14/09/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Lo example
```{r}
library(tidyverse)
library(readxl) #this package let us read an excel file into R
library(here)
library(ggpubr)
library(emo)
```

Read the excel file

```{r}
Kali_rtpcr_data_raw <- read_xlsx(here("slides","02-wrangle_visualise_rtqPCR","data", "qPCR_HCT116plus_n3_KG.xlsx")
                                 ,skip=1,col_names = TRUE,
sheet = 1) 
Kali_rtpcr_data_raw 
Kali_rtpcr_data<-
  Kali_rtpcr_data_raw %>% select(1,2,4,5,7,8) %>% drop_na()
```

This is definitely no a Tidy data! To get to tidy data we need:
1) Column with exp condition
2) Colum with relative expression
3) Column with replicate 
4) Comparisons

There are several ways we could format the data to get to that point. Since this is a pretty untidy but small dataset One lazy way would be to reate a tibble from scratch:

```{r}
Kali_tibble_2_3<-
Kali_rtpcr_data %>% select(1,3,5) %>% pivot_longer(everything(),names_to = "condition",values_to="expression") %>% mutate(replicate=rep(c(1,2,3),5)) %>% 
  select(-condition)

Kali_tibble_1<-
Kali_rtpcr_data %>% select(2,4,6) %>% pivot_longer(everything(),names_to = "nonneeded",values_to="condition") %>% select(-nonneeded)


groupping<-c(rep(1,6),rep(2,9)) 
Kali_table<-cbind(Kali_tibble_1,Kali_tibble_2_3,groupping)
Kali_tibble<-Kali_table %>% as_tibble() %>% 
    mutate(condition = case_when(
      condition=="LNA A" ~ "A LNA",
       condition=="C1 si" ~ "si C1",
      TRUE~condition)) %>% 
      
  mutate_if(is.character,as.factor)
```
Kali_tibble is a tidy tibble! `r emo::ji("smile")`


```{r}
Kali_tibble_LNA<-
  Kali_tibble %>% filter(groupping==2) 

Kali_tibble_C<-
  Kali_tibble %>% filter(groupping==1)

```

```{r}
Kali_tibble_C %>% 
  mutate_if(is.character,as.factor) %>% 
 ggboxplot( x = "condition", y = "expression",
          color = "condition", palette = "jco",
          add = "jitter")+ylim(0,2)+  
  stat_compare_means(method = "t.test",label.y = 1.5)
  

Kali_tibble_LNA %>% 
  mutate_if(is.character,as.factor) %>% 
 ggboxplot( x = "condition", y = "expression",
          color = "condition", palette = "jco",
          add = "jitter")+ylim(0,2)+  
    stat_compare_means(label = "p.signif", method = "t.test",
                       ref.group = "A LNA") 
```


