---
title: "05_correlation_replicates_Proteomics"
author: "Maria Dermit"
date: "10/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading libraries
```{r}
library(tidyverse)
# install.packages("corrplot")
library(corrplot) #to easily add statistical summaries in ggplot-like plots
library(here) #to add paths
#install.packages("Hmisc")
library(Hmisc) # for rcorr
#install.packages("broom")
library(broom) #for tidiness
```
### Reading data. 
These are proteomics data where I have 2 technical replicates per condition and two sample types- bodies and protrusions. I expect a high correlation across technical replicates. 

```{r}
proteinGroups_raw<-read_delim(here("slides","05-correlation","data", "proteinGroups_2h_methodpaper.txt"), delim="\t")
names(proteinGroups_raw)
```

This is the output of Maxquant, that comes with lots of information about peptides. Here I am selecting columns I want:
```{r}
proteinGroups<-proteinGroups_raw %>%
    select(7,43:46,61:63) %>% 
    filter(is.na(`Only identified by site`) & is.na(Reverse),is.na(`Potential contaminant`)) %>% 
select(starts_with("Reporter")) %>% 
  rename(Body_R1="Reporter intensity corrected 1 1",
         Body_R2= "Reporter intensity corrected 2 1",
         Prot_R1="Reporter intensity corrected 1 2",
         Prot_R2= "Reporter intensity corrected 2 2")
```


### EDA
Initially we want to check whether these data follow a normal distribution. 
```{r}
summary(proteinGroups)
```

We can show the distribution tor example for the first sample: 
```{r}
proteinGroups %>% 
  ggplot(aes(x=Body_R1))+geom_histogram()
```
Is not normally distributed. We need to log the data to get a normal distribution.

```{r}
proteinGroups_log<-proteinGroups %>% log2()
```

```{r}
proteinGroups_log %>% 
  ggplot(aes(x=Body_R1))+geom_histogram()
```

We need to subtract the median to center distribution to 0. This is standard procedure when we are analyzing proteomics data.
```{r}
colmed<-apply(proteinGroups_log,2,median)
final_prot<-proteinGroups_log - colmed
```
All samples are centered to 0.

We can plot all the the columns/samples and check that they are all normally distributed. 
```{r}
final_prot%>%
  gather() %>%                             # Convert to key-value 
  ggplot(aes(value)) +                     # Plot the values
    facet_wrap(~ key, scales = "free") +   # In separate panels
    geom_density() 
```
They all seem to follow a normal distribution.


Now we can check correlation
```{r}
cor.test(proteinGroups_log$Body_R1, proteinGroups_log$Body_R2, method="pearson")
```
What is the problem? Hint there are -Inf values in the data.  

```{r}
lix <- is.infinite(proteinGroups_log$Body_R1) | is.infinite(proteinGroups_log$Body_R2) 
cor.test(proteinGroups_log$Body_R1[!lix], proteinGroups_log$Body_R2[!lix], method="pearson")
```
This works, but it does output a non-tidy format

```{r}
as.matrix(cbind(proteinGroups_log$Body_R1[!lix], proteinGroups_log$Body_R2[!lix])) %>% 
    rcorr(type = "pearson")  %>% 
  tidy()
```
There is a high correlation and no significant difference between both samples. 
We can also use the `corrplot` function to  
```{r}
lix <- is.infinite(proteinGroups_log$Body_R1) | is.infinite(proteinGroups_log$Body_R2)| is.infinite(proteinGroups_log$Prot_R1) | is.infinite(proteinGroups_log$Prot_R2)
res <- cor(proteinGroups_log[-which(lix),],method = c("pearson"))
library(corrplot)
corrplot(res, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```
